Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-06-26 paper.tex
Remove corresponding author
Add hyperlink to abstract

\begin{abstract}
This paper describes an approach for developing strategic cycle network
planning tools. Based on our experience developing and deploying the
Cycle Route Uptake and Scenario Estimation (CRUSE) Tool for Ireland, we
outline the underlying methods, including disaggregation of
origin-destination data with the open source `odjitter' software,
incorporation of additional trip purposes, routing, scenario generation,
and development of an intuitive user interface that is tested and used
by practitioners. Commissioned by the national infrastructure agency
Transport Infrastructure Ireland, CRUSE provides estimates of current
and potential future cycling levels under `snapshot' scenarios to inform
investment decisions. The publicly available results at
https://cruse.bike/ enable planners, engineers, and other stakeholders
to make more evidence-based decisions. CRUSE goes beyond previous work
by: modeling networks at high spatial resolution; simulating multiple
trip purposes (social, shopping, personal utility, recreational, and
cycle touring), supplementing official origin-destination datasets on
travel for work and education; and providing estimates of `quietness' (a
proxy for cyclist comfort and route preference) at the route segment
level. Three network types --- `Fastest', `Balanced', and `Quietest' ---
help plan both arterial and residential cycle networks. Workshops and
unstructured interviews with stakeholders were used to inform the
development of the tool. Feedback shows that the tool has a wide range
of uses and is already being used in practice to inform urban,
inter-urban, and rural cycle network designs. The approach is flexible
and open-source, allowing the underlying ideas and code to be adapted,
supporting more evidence-based and effective cycling policies and
interventions internationally.
\end{abstract}

@@

The first two workshops took place in May 2022, during which the tool
was introduced to key staff involved in cycle network planning in
Kildare and Limerick counties. The county-specific approach allowed the
workshop to focus on specific areas and key corridors. The local
transport planners were asked to provide feedback in a semi-structured
interview approach, with questions on the evidence they currently have
access to, how they may be able to use the tool, and requests for new
features. The third and final workshop took place on the
7\textsuperscript{th} December 2023 and included descriptions of recent
changes to the tool, with an aim being to get feedback on the new
recreational and cycle touring evidence, with representatives from
county-level transport planning bodies, Sport Ireland, and Waterways
Ireland.

@@

Instead of trying to show such use cases, of which there are many
hundreds, we present a selection of results to illustrate the main
features of the resulting evidence, in Section~\ref{sec-quantiative}. We
also present some qualitative results based on workshops and interviews
with stakeholders in Ireland, in Section~\ref{sec-qualitative}.

@@

{A final limitation of the approach relates to \emph{how} it was
developed. As described in Section~\ref{sec-stakeholder-engagement}, the
development of the tool was participatory, but only insofar as people
who attended our workshops could provide feedback. The people who did
provide feedback were deliberately chosen as the target audience. In
future work we would like to collect feedback from a wider range of
people, including campaigners, service providers (e.g.~staff involved in
travel planning for schools and new developments), and people who not
involved in the planning process.}

>>>>

\begin{abstract}
This paper describes an approach for developing strategic cycle network
planning tools. Based on our experience developing and deploying the
Cycle Route Uptake and Scenario Estimation (CRUSE) Tool for Ireland, we
outline the underlying methods, including disaggregation of
origin-destination data with the open source `odjitter' software,
incorporation of additional trip purposes, routing, scenario generation,
and development of an intuitive user interface that is tested and used
by practitioners. Commissioned by the national infrastructure agency
Transport Infrastructure Ireland, CRUSE provides estimates of current
and potential future cycling levels under `snapshot' scenarios to inform
investment decisions. The publicly available results at
\url{https://cruse.bike/} enable planners, engineers, and other
stakeholders to make more evidence-based decisions. CRUSE goes beyond
previous work by: modeling networks at high spatial resolution;
simulating multiple trip purposes (social, shopping, personal utility,
recreational, and cycle touring), supplementing official
origin-destination datasets on travel for work and education; and
providing estimates of `quietness' (a proxy for cyclist comfort and
route preference) at the route segment level. Three network types ---
`Fastest', `Balanced', and `Quietest' --- help plan both arterial and
residential cycle networks. Workshops with stakeholders were used to
inform the development of the tool. Feedback shows that the tool has a
wide range of uses and is already being used in practice to inform
urban, inter-urban, and rural cycle network designs. The approach is
flexible and open-source, allowing the underlying ideas and code to be
adapted, supporting more evidence-based and effective cycling policies
and interventions internationally.
\end{abstract}

@@

The first two workshops took place in May 2022, during which the tool
was introduced to key staff involved in cycle network planning in
Kildare and Limerick counties. The county-specific approach allowed the
workshop to focus on specific areas and key corridors. During the
workshops, after the tool was introduced and presented, participants
were asked questions in a semi-structured interview format, with
questions on the evidence they currently have access to, how they may be
able to use the tool, and requests for new features. The third and final
workshop took place on the 7\textsuperscript{th} December 2023 and
included descriptions of recent changes to the tool, with an aim being
to get feedback on the new recreational and cycle touring evidence, with
representatives from county-level transport planning bodies, Sport
Ireland, and Waterways Ireland.

@@

Instead of trying to show such use cases, of which there are many
hundreds, we present a selection of results to illustrate the main
features of the resulting evidence, in Section~\ref{sec-quantiative}. We
also present some qualitative results based on workshops with
stakeholders in Ireland, in Section~\ref{sec-qualitative}.

@@

A final limitation of the approach relates to \emph{how} it was
developed. As described in Section~\ref{sec-stakeholder-engagement}, the
development of the tool was participatory, but only insofar as people
who attended our workshops could provide feedback. The people who did
provide feedback were deliberately chosen as the target audience. In
future work we would like to collect feedback from a wider range of
people, including campaigners, service providers (e.g.~staff involved in
travel planning for schools and new developments), and groups who are
under-represented in transport planning processes.
